%!TEX root = ../thesis.tex
%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

%\begin{flushright}{\slshape    
%    We have seen that computer programming is an art, \\ 
%    because it applies accumulated knowledge to the world, \\ 
%    because it requires skill and ingenuity, and especially \\
%    because it produces objects of beauty.} \\ \medskip
%    --- \defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974} \citep{knuth:1974}
%\end{flushright}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
This work presented in this thesis is the result of the last seven years. I wish to thank all the people who have supported and helped me during this long period of time. Without them this work would not have been finished sucessfully.
\\\\
I would like to thank Prof. Dr. Bernhard Humm for his support, his brilliant ideas that pushed the thesis forward, his patience, when the progress has been slow and his advices.
\\\\
I would also like to thank Prof. Dr. Udo Bleimann, for his advices regarding the research process in general and his support.
\\\\
Additionally, I would like to thank Prof. Paul S. Dowland for his help to improve my academic writing skills and for his advice regarding the graduate school formalities.
\\\\
I would sincerly like to thank my girlfriend Nadine for her endless support, love and for keeping things running. She has always believed in me und supported me when times were tough. Without her, this work would not have been possible.
\\\\
Special thanks to Pumi and Mausi, my two cats, for always reminding me of the really important things in live: eating, napping, playing and having a clean litter box.
\\\\
Last but not least, I would like to thank my family for their love and their support.

\endgroup



