%!TEX root = ../thesis.tex
%******************************************************************************
\chapter{Introduction}\label{ch:introduction}
%******************************************************************************

Enterprise Systems like customer-billing systems or financial transaction systems are required to process large volumes of data in a fixed period of time. For example, a billing system for a large telecommunication provider has to process more than 1 million bills per day.
Those systems are increasingly required to also provide near-time processing of data to support new service offerings.

Traditionally, enterprise systems for bulk data processing are implemented as batch processing systems \citep{Fleck:1999aa}. Batch processing delivers high throughput but cannot provide near-time processing of data, that is the end-to-end latency of such a system is high. End-to-end latency refers to the period of time that it takes for a business process, implemented by multiple subsystems, to process a single business event.  For example, consider the following billing system of a telecommunications provider:
\begin{itemize}
	\item Customers are billed once per month
	\item Customers are partitioned in 30 billing groups
	\item The billing system processes 1 billing group per day, running 24h under full load.
\end{itemize}
In this case, the mean time for a call event to be billed by the billing system is 1/2 month. That is, the mean end-to-end latency of this system is 1/2 month.

A lower end-to-end latency can be achieved by using single-event processing, for example by utilizing a message-oriented middleware for the integration of the services that form the enterprise system. While this approach is able to deliver near-time processing, it is hardly capable for bulk data processing due to the additional communication overhead for each processed message. Therefore, message-based processing is usually not considered for building a system for bulk data processing requiring high throughput.

The processing type is usually a fixed property of an enterprise system that is decided when the architecture of the system is designed, prior to implementing the system. This choice depends on the non-functional requirements of the system. These requirements are not fixed and can change during the lifespan of a system, either anticipated or not anticipated.

Additionally, enterprise systems often need to handle load peaks that occur infrequently. For example, think of a billing system with moderate load over most of the time, but there are certain events with very high load such as New Year's Eve. Most of the time, a low end-to-end latency of the system is preferable when the system faces moderate load. During the peak load, it is more important that the system can handle the load at all. A low end-to-end latency is not as important as an optimized maximum throughput in this situation.

\section{Aims and Objectives of the Research}\label{sec:research_objectives}
This research project aims to find a solution for the following problem:
\begin{quote}
\textbf{How to achieve high-performance near-time processing of bulk data?}
\end{quote}

Based on this problem, the thesis aims to answer the following research questions:
\begin{itemize}
	\item \textbf{RQ1:} What are the performance characteristics of batch and single-event processing systems?
	\item \textbf{RQ2:} What is the impact of data granularity on end-to-end latency and maximum throughput?
	\item \textbf{RQ3:} tbd.
	\item \textbf{RQ4:} tbd.
\end{itemize}

To approach these research questions, the research project has the following key objectives:
\begin{enumerate}
	\item Performance evaluation of batch and messaging systems regarding throughput and latency.
	\item Development of a concept for an adaptive middleware that delivers low latency while providing high throughput.
	\item Implementation of a research prototype used for demonstrating the practicability of the concept.
	\item Specification and conduction of appropriate performance tests to evaluate the developed approach.
	\item Development of a conceptional framework containing guidelines and rules for the practitioner how to implement an enterprise system based on the adaptive middleware for near-time processing of bulk data.
\end{enumerate}

\section{Research Methodology}

\begin{itemize}
	\item Evaluation of current approaches to optimize the performance of service-oriented systems. 
	\item To better understand the performance characteristics of batch and message-based processing two prototypes of each processing styles has been implemented.
	\item Using these prototypes, a performance evaluation has been done to better understand the differences between the two processing styles, with a special focus on the latency and throughput.
	\item Using the message-based prototype, the impact of data granularity on latency and throughput has been studied.
	\item Based on the results of the performance evaluation the concept of an adaptive middleware has been developed.
	\item The message-based prototype has been extending to implement the concepts of the adaptive middleware.
	\item A performance evaluation has been conducted to evaluate the proposed concepts for an adaptive middleware for bulk data processing.
\end{itemize}

\section{Contributions}\label{sec:contributions}

\begin{itemize}
	\item Performance evaluation of batch and messaging systems regarding throughput and latency
	\item Concept and prototype implementation of an adaptive middleware 
	\item Conceptional Framework
\end{itemize}

\section{Outline of the Thesis}\label{sec:thesis_outline}

\begin{enumerate}
	\item Introduction
	\item Background
	\item Related Work
	\item Performance Evaluation of Batch and Message-based Systems
	\item An Adaptive Middleware for Near-Time Processing of Bulk Data
	\item A Conceptual Framework For Feedback-Controlled Bulk Data Processing Systems
	\item Conclusion
\end{enumerate}