%!TEX root = ../thesis.tex
%******************************************************************************
\chapter{Source Code}\label{ch:appendix_source_code}
%******************************************************************************

This section describes the source code of the research prototypes, which have been implemented during the course of this research.
\\\\
The complete source code is available on Github:\\
https://github.com/mswiente/phd\_prototype

\section{Project Structure}

The source code is organized in the following modules:

\begin{itemize}
\item \textbf{BatchProcessor}\\
Contains the implementation of the batch prototype based on Spring Batch.
\item \textbf{BillingRouter}\\
Contains the implementation of the messaging prototype based on Apache Camel.
\item \textbf{CamelUtils}\\
Contains common Apache Camel specific logging utilities
\item \textbf{DataGenerator}\\
Contains the load generator.
\item \textbf{FunctionalCore}\\
Contains the common business functionality of the system used by batch and messaging prototypes.
\item \textbf{MediationBatchRoute}\\
Contains the wrapper to integrate the mediation processor of the batch prototype with Apache Camel.
\item \textbf{MediationService}\\
Contains the webservice wrapper of mediation processor used by the messaging prototpye.
\item \textbf{PerformanceMonitor}\\
Contains the Feedback-Control framework to monitor, measure and control the messaging system.
\item \textbf{RatingBatchRoute}\\
Contains the wrapper to integrate the rating processor of the batch prototype with Apache Camel.
\item \textbf{RatingService}\\
Contains the webservice wrapper of the rating processor used by the messaging system.
\end{itemize}